Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-04-03 parts/figures.tex
added remark for bluring, fixes #31

\begin{figure*}
\inclGrid{spl-input}
\caption{Nine of the lens candidates marked up with spaghetti
  diagrams.  Red, blue and green dots are proposed locations for
  maxima, minima and saddle points of the arrival time respectively.
  The curves help guide the placement of the dots, but their precise
  appearance has no significance.  This selection includes the
  best-modelled systems, but also one case (SW57 at upper right) of
  unsuccessful modelling.  Since the modelling process is
  collaborative among the volunteers, with anyone welcome to
  contribute new models or modify existing ones, there are variant
  spaghetti diagrams for all the modelled systems.  The online
  supplement displays all the models presented for discussion during
  this work.
\label{fig:splinput}}
\end{figure*}

@@

\begin{figure*}
\inclGrid{nsynth}
\caption{Synthetic images of the systems from
  Figure~\ref{fig:splinput}, derived from the lens models.  The
  reconstructed lensed features are keep the Space~Warps false-colour
  scheme from Figures~\ref{fig:splinput}.  The rest has been changed
  to black-and-white.
  \label{fig:synth}}
\end{figure*}

>>>>

\begin{figure*}
\inclGrid{spl-input}
\caption{Nine of the lens candidates marked up with spaghetti
  diagrams.  Red, blue and green dots are proposed locations for
  maxima, minima and saddle points of the arrival time respectively.
  The curves help guide the placement of the dots, but their precise
  appearance has no significance.  This images are screenshots from the 
  SpaghettiLens user interface, which applies interpolation to background
  images. The scaling is adjusted to fit the other images.
  This selection includes the
  best-modelled systems, but also one case (SW57 at upper right) of
  unsuccessful modelling.  Since the modelling process is
  collaborative among the volunteers, with anyone welcome to
  contribute new models or modify existing ones, there are variant
  spaghetti diagrams for all the modelled systems.  The online
  supplement displays all the models presented for discussion during
  this work.  
\label{fig:splinput}}
\end{figure*}

@@

\begin{figure*}
\inclGrid{nsynth}
\caption{Synthetic images of the systems from
  Figure~\ref{fig:splinput}, derived from the lens models.  The
  reconstructed lensed features keep the Space~Warps false-colour
  scheme from Figures~\ref{fig:splinput}.  The rest has been changed
  to black-and-white. 
  \label{fig:synth}}
\end{figure*}
